No proof nets for \capsabbrev{mll} with units\\[5pt]\Large Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete

### 2014-01-20 main/LICS.tex
Fix orphaned QED symbol
Upgrade IEEEtran.cls to the latest version, which supports manual
placement of the QED symbol.
re-wording for better spacing
star-autonomous blablabla

@@

\begin{proposition}[\cite{Danos-Regnier-1989}]
\label{prop:correctness and sequentialisation}
%
For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
%
For a net $\links$ for $\Gamma$, there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (\emph{sequentialisation}).
%
\end{proposition}

@@

	\item
The link from $i$ is re-attached to $v$ to yield the final configuration.
%
\displayOcto{\octorollA2}

\end{enumerate}
\end{IEEEproof}

>>>>

The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008} for \capsabbrev{mll} without units).
%
Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two representations denote the same morphism in any star-autonomous category.

@@

\begin{proposition}[\cite{Danos-Regnier-1989}]
\label{prop:correctness and sequentialisation}
%
%
If $\Pi\toNet\links$ and $\Pi$ has conclusion $\Gamma$, then $\links$ is a proof net for $\Gamma$.
%For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
%
For a net $\links$ for $\Gamma$, there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (\emph{sequentialisation}).
%
\end{proposition}

@@

	\item
The link from $i$ is re-attached to $v$ to yield the final configuration.
%
\displayOcto{\octorollA2\IEEEQEDhere}
\end{enumerate}
\end{IEEEproof}
